Eurovision Song Contest: semifinal 1, 2009

### 2022-07-13 inst/eurovision.Rmd
use sticker in Rmd
start work on Eurovision

```{r,morestuff}
eurovision <- hyper2()

@@

>>>>

```{r,morestuff,cache=TRUE}
eurovision <- hyper2()

@@

## Testing nonindependence using `hyper3` idiom

First we use `hyper2`:

```{r,label=loadeurohyper2,cache=TRUE}
a <- read.table("euro_ranks.txt",header=TRUE)
jj <- table(a$country)
wanted_countries <- names(jj[jj >= 10])
a <- a[a$country %in% wanted_countries,]
H <- hyper2()
for(y in unique(a$year)){
   H <- H + race((a$country)[a$year == y])
}
H
```

Find the evaluate:

```{r,findhyper2euroevaluate,cache=TRUE}
mH <- maxp(H)
```

```{r,plotmH}
dotchart(mH)
```

Now use `hyper3` and follow `RB_BB_LF()` in
`plackett_luce_monster.Rmd`
